Resource Adequacy and Operational Security Interaction in the EPOC 2030-50 Project

### 2022-05-18 papers/main.tex
Updating scripts

\title{Description of a Deterministic Unit Commitment Model with Probabilistic Reserve constraints and Network Representation}

@@

\section{Model description}

@@

>>>>

\title{Resource Adequacy and Operational Security Interaction in the EPOC 2030-50 Project}

@@

\section{Description of a Deterministic Unit Commitment Model with Probabilistic Reserve (DUC-PR) constraints}

@@

\section{Input data - stylised Belgian grid with a large amount of renewables}

\section{Analysis of DUC-PR model results}

This analysis relates only to the 309th day of the year (November 5th).

\subsection{No operating reserves}

\begin{table}
    \begin{tabular}{ccccc}
        \toprule
        UC  & DANet & PSCD & Load shedding [MWh] & Objective \\
            &       &      & 0.0                 & 101,916 \\
        \xm &       &      & 0.0                 & 212,558 \\
        \xm & \xm   &      & 0.0                 & 252,327 \\
        \xm & \xm   & \xm  & 0.0                 & 252,327 \\
    \end{tabular}
    \caption{Analysis of model results when operating reserves are not included. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simulataneous Charging and Discharging constraints.}
\end{table}
